\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2021-11-23 main.tex

\subsection{Pearl vortices in thin films}
\label{section:examples:pearl-vortices}
Vortices trapped in 2D superconductors ($d\ll\lambda$, where $d$ is the film thickness and $\lambda$ is the London penetration depth), i.e. ``Pearl vortices,'' are associated with different current and magnetic field distributions than Abrikosov vortices trapped in bulk type-II superconductors~\cite{Pearl1964-cl}. The 2D Fourier transform $\tilde{H}_z(\vec{k}, z)$ of the out-of-plane component of the magnetic field $H_z(\vec{r}, z)$ from a Pearl vortex located at the origin $x=y=z=0$ is given by

\begin{equation}
    \tilde{H}_z(\vec{k}, z)=\mathcal{F}\{H_z(\vec{r}, z)\}=\frac{1}{\mu_0}\frac{\Phi_0e^{-|\vec{k}|z}}{1+2\Lambda|\vec{k}|},
    \label{eq:pearl}
\end{equation}
where $\mathcal{F}\{\cdot\}$ is the 2D Fourier transform, $\vec{k}=(k_x, k_y)$ are in-plane spatial frequencies, $z$ is the out-of-plane position at which the field is evaluated, and $2\Lambda = 2\lambda^2 / d$ is the Pearl length~\cite{Pearl1964-cl, Tafuri2004-ap}. The real-space magnetic field distribution near a Pearl vortex can be calculated numerically by taking the inverse Fourier transform of Eq.~\ref{eq:pearl}: $H_z(\vec{r}, z)=\mathcal{F}^{-1}\{\tilde{H}_z(\vec{k}, z)\}$. The field distributions generated by \SuperScreen in the presence of vortices as described in Sections~\ref{section:model:vortices} and~\ref{section:implementation} agree to within a few percent with the distributions obtained using this Fourier transform method, as demonstrated in Code Block~\ref{code:pearl-vortex} and Figure~\ref{fig:pearl}(c-e).

To include vortices in a \SuperScreen model, one can simply input a \inline{list} of \inline{superscreen.Vortex} objects when calling \inline{superscreen.solve()} (see Code Block~\ref{code:pearl-vortex}). A \inline{Vortex} object specifies the $x,y$ position for the vortex core, the name of the superconducting layer in which the vortex is pinned, and the number of flux quanta $\Phi_0$ contained in the vortex (which is 1 by default). See Ref.~\cite{Brandt2005-wj} for a method to compute the self-energy and interaction energies of vortices in thin films.

@@

\begin{figure*}[h]
    \centering
    \includegraphics[width=\textwidth]{examples/images/pearl.png}
    \caption{Vortex field profiles calculated with \SuperScreen agree with the analytical solution (Eq.~\ref{eq:pearl}) to within a few percent. Here, we model a vortex trapped at the center of a square superconducting film lying in the $x-y$ plane with side length $20\,\um$ as a function of the film's effective penetration depth, $\Lambda$. (a) Cross section along the $x$-axis of the out-of-plane magnetic field $\mu_0H_z$ from the vortex, evaluated at a vertical distance $z=1\,\um$ above the film. The inset shows the vortex field profile for $\Lambda=0\,\um$ evaluated at $z=1\,\um$, with a dashed white line indicating the cross-section axis. (b) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $x$-axis cut shown in (a). (c) Cross-section along the $z$-axis of $\mu_0H_z$ directly above the center of the vortex (logarithmic $y$ axis scale). (d) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $z$-axis cut shown in (c). In (a) and (c), the results from \SuperScreen are shown as open circles and the results from the Fourier transform method are shown as solid lines. (e) The fluxoid $\Phi_S^f$ for a circular region in the film with radius $r=1\,\um$ centered on the vortex core. As $\Lambda$ increases, so to does the supercurrent contribution to the fluxoid. (f) Error in the total simulated fluxoid relative to $\Phi_0$: $(\Phi_S^f(\Lambda) - \Phi_0) / \Phi_0$.}
    \label{fig:pearl}
\end{figure*}

@@

Figure~\ref{fig:pearl}(e) shows the fluxoid for a circular region $S$ with radius $r=1\,\um$ enclosing a Pearl vortex trapped in a film as a function of the film's effective penetration depth, $\Lambda$. When $\Lambda=0$, the screening currents decay very quickly away from the center of the vortex, so the ``supercurrent part'' of the $\Phi^f_S$ vanishes. With increasing $\Lambda$, the ``supercurrent part'' accounts for an increasing fraction of the total fluxoid.
% See \ref{appendix:fluxoid} for a demonstration of the fluxoid properties listed in Section~\ref{section:model:fluxoid}.

@@

\subsection{Self-inductance and mutual inductance}
\label{section:examples:mutual-inductance}

As shown in Ref.~\cite{Brandt2005-wj}, the mutual inductance $M_{ij}$ between holes $i$ and $j$ in a superconducting structure is given by
\begin{equation}
    M_{ij}=\frac{\Phi^f_{S_i}}{I_j},
\end{equation}
where $\Phi^f_{S_i}$ is the fluxoid for a region $S_i$ containing the hole $i$, and $I_j$ is the current circulating around hole $j$. The mutual inductance values for a set of holes form a mutual inductance matrix. The diagonals of the mutual inductance matrix are the hole self-inductances ($M_{ii}=L_i$, the self-inductance of hole $i$), and the matrix is symmetric ($M_{ij}=M_{ji}$) due to the reciprocity theorem. If the penetration depth of the film containing hole $i$ is $\Lambda = 0$, then no field penetrates the film and the fluxoid $\Phi^f_{S_i}$ is equal to $\Phi_i$, the flux through hole $i$.

For a circular ring with inner radius $a$, outer radius $b>a$, and penetration depth $\Lambda=0$, Clem~\cite{Babaei_Brojeny2003-la} found that the self-inductance approaches $L=2\mu_0 a$ in the ``small hole'' limit $\tilde{a}=a/b\ll 1$. Clem and Brandt~\cite{Brandt2004-ew} and Khapaev~\cite{Khapaev1997-kw} calculated the self-inductance of circular and square rings as a function of the ratio of inner and outer diameters.

\subsection{Application: scanning SQUID microscopy}
\label{section:examples:scanning-squid}

In scanning superconducting quantum interference device (SQUID) susceptometry, the diamagnetic susceptibility of a superconducting sample is measured by bringing the sample close to a pair of superconducting loops. The first loop, called the ``pickup loop" is attached to a SQUID circuit that sensitively measures the magnetic flux threading the loop. The second loop, called the ``field coil," carries a known current and applies a known magnetic field to both the pickup loop and the sample. The superconducting sample screens the magnetic field from the field coil, modifying the amount of flux threading the pickup loop. Thus the mutual inductance between the field coil and pickup loop provides a measure of the sample's magnetic susceptibility. For superconducting samples, this diamagnetic response is a measure of the sample's penetration depth and therefore its superfluid density.

Analysis developed to interpret the results of scanning SQUID susceptometry measurements makes several simplifying assumptions that are not always satisfied: 1) the sample's effective penetration depth $\Lambda$ (or Pearl length $2\Lambda$) is spatially homogeneous, 2) the sample is much larger than the field coil, and 3) the field coil and pickup loop can be approximated as one-dimensional coaxial, coplanar circular loops~\cite{Kirtley_Kalisky_2012}.

% \begin{figure}[!h]
% \centering
% \begin{subfigure}{.35\textwidth}
%   \centering
%   \includegraphics[width=\linewidth]{examples/images/squid_susceptometry/squid_with_sample_mesh.png}
%   \label{fig:squid_mesh}
%   \caption{}
% \end{subfigure}%
% \hspace{10pt}
% \begin{subfigure}{.5\textwidth}
%   \centering
%   \includegraphics[width=\linewidth]{examples/images/squid_susceptometry/squid_with_sample_M0_convergence.png}
%   \label{fig:squid_convergence}
%   \caption{}
%   \caption{Fractional change in flux though all polygons vs. solver iteration with a current of $1\,\mathrm{mA}$ flowing in the field coil (\inline{fc}). The mutual inductance $M_0$ is given by the flux through the pickup loop (\inline{pl_hull}) divided by the field coil current.}
% \end{subfigure}%
% \caption{(a): Device polygons and mesh for the SQUID susceptometer model. (b) Fractional change in flux though all polygons vs. solver iteration with a current of $1\,\mathrm{mA}$ flowing in the field coil (\inline{fc}). The mutual inductance $M_0$ is given by the flux through the pickup loop (\inline{pl_hull}) divided by the field coil current.}
% \label{fig:susceptometry}
% \end{figure}

Figure~\ref{fig:squid-mutuals}(a) shows \SuperScreen \inline{Device} models of the field coil and pickup loop region of four types of real SQUID susceptometers, with geometry taken from the layout artwork (GDS) files. In addition to the field coil and pickup loop, there are superconducting shields that limit the amount of magnetic flux that can penetrate the leads connecting the loops to the rest of the circuit (the rest of the circuit is not modeled). There are three relevant layers of superconducting films: the base electrode (``BE"), which is furthest from the sample contains the field coil; the first wiring layer (``W1"), which contains the pickup loop and a shield covering the field coil leads; and the second wiring layer (``W2"), which is closest to the sample and contains a shield covering the pickup loop leads. There are two insulating layers: I1, which separates BE and W1, and I2, which separates W1 and W2. Table~\ref{table:squid-layers}.

\begin{table*}[]
\centering
\begin{tabular}{|l|l|l|l|l|}
\hline
Layer name & Material & Thickness & Vertical position, $z_0$ & Films located in layer \\ \hline
\hline
W2 & Nb & $d_\mathrm{W2} = 200\,\nm$ & $d_\mathrm{W2} / 2$ & Pickup loop shield, modulation coil \\ \hline
I2 & SiO${}_2$ & $d_\mathrm{I2} = 130\,\nm$ & --- & --- \\ \hline
W1 & Nb & $d_\mathrm{W1} = 100\,\nm$ & $d_\mathrm{W2} + d_\mathrm{I2} + d_\mathrm{W1} / 2$ & Pickup loop, field coil shield \\ \hline
I1 & SiO${}_2$ & $d_\mathrm{I1} = 150\,\nm$ & --- & --- \\ \hline
BE & Nb & $d_\mathrm{BE} = 160\,\nm$ & $d_\mathrm{W2} + d_\mathrm{I2} + d_\mathrm{W1} + d_\mathrm{I1} + d_\mathrm{BE} / 2$ & Field coil, pickup loop shield \\ \hline
\end{tabular}
\caption{Layer stackup for the SQUID susceptometers Section~\ref{section:examples:scanning-squid}. W2 is located at the surface of the chip (deposited last, closest to the sample) and BE deepest below the chip's surface (deposited first). See Ref.~\cite{Kirtley2016-zz} for more details on the designed of the suscpetometers.}
\label{table:squid-layers}
\end{table*}

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{examples/images/squid-mutuals.png}
    \caption{Calculating SQUID susceptometer mutual inductance, defined as the fluxoid induced in the SQUID pickup loop per unit current flowing in the field coil: $M=\Phi_\mathrm{PL} / I_\mathrm{FC}$. Top row (a): Schematics of \SuperScreen models for the field coil and pickup loop region of four sizes of scanning SQUID susceptometer (generated using \inline{Device.draw()}) with pickup loop inner radii ranging from $0.1\,\um$ (``Small'') to $3\,\um$ (``X-Large''). The wiring layers BE, W1, and W2 are shown in blue, orange, and green respectively. Middle row (b): Simulated magnetic field $\mu_0H_z$ evaluated at the plane of layer W1, which contains the pickup loop, normalized by the current $I_\mathrm{FC}$ flowing in the field coil (which is located in layer BE). Bottom row (c): Convergence of the four models, defined as the fractional change in mutual inductance between subsequent iterations $i$. For all four models, the simulated mutual inductance, $M_\mathrm{sim}$, falls within the range of mutual inductance values measured in real devices, $M_\mathrm{exp}$, which were reported in Table 1 of Ref.~\cite{Kirtley2016-zz}. The meshes for the ``Small,'' ``Medium,'' and ``Large'' models consisted of approximately 5,000 vertices and 10,000 triangles, whereas the mesh for the ``X-Large'' model consisted of about 7,700 vertices and 15,000 triangles. The two smaller models converge more quickly than the two larger models for reasons discussed in \ref{appendix:numerics}. Note that for the ``X-Large'' model, we set the thicknesses of layers I1 and I2 both to 300 nm to ensure convergence (see \ref{appendix:numerics} and Figure~\ref{fig:xlarge-dz-dr}).}
    \label{fig:squid-mutuals}
\end{figure*}

To model a SQUID susceptometry measurement, we first calculate $M_0$, the mutual inductance between the field coil and pickup loop in the absence of the sample. This can be done by temporarily setting the sample layer effective penetration depth to a very large value such that it essentially does not screen the field from the field coil (in this case, we set $\Lambda = 10^5\,\um$). We then model the field from a known current flowing in the field coil following Section~\ref{section:model:holes} and self-consistently calculate the response of both the sample and the other superconducting layers of the SQUID sensor following Section~\ref{section:model:multilayer}. To ensure that the 2D current distribution in the field coil is approximately uniform (as we would expect for a real applied current), we set the field coil layer effective penetration depth to be greater than the width of the field coil conductor.

Once $M_0$ is known, we can ``turn on" the sample's diamagnetic response by setting its effective penetration depth $\Lambda$ to the desired value and compute $M(z, \Lambda)$ for a given vertical distance $z$ between the sample and the SQUID as described in the previous paragraph. The SQUID susceptibility signal is then $M(z, \Lambda) - M_0$, the change in mutual inductance between the field coil and pickup loop due to the presence of the sample (usually given in units of $\Phi_0/\mathrm{A}$, where $\Phi_0$ is the superconducting flux quantum). The susceptibility can also be normalized to the bare mutual inductance $M_0$, giving a dimensionless susceptibility $\chi(z, \Lambda)=[M(z, \Lambda) - M_0] / M_0$.

@@

Third, \SuperScreen does not support ``terminal currents,'' i.e. currents flowing in one terminal of a device and out another terminal. This means that inductance calculations are limited to structures with holes, in which all applied currents are circulating currents associated with trapped flux (see Sections~\ref{section:model:holes} and~\ref{section:examples:mutual-inductance}). Terminal currents can, however, be included in stream function-base models by setting appropriate boundary conditions~\cite{Khapaev1997-kw,Khapaev2001-xq,Khapaev2001-pw,Muller2021-ci}. Finally, care should be taken to ensure that for a given model the mesh is of sufficient density that, to within the desired precision, the results of simulations do not depend on mesh size (see \ref{appendix:numerics}).

@@

\begin{figure*}[h]
    \centering
    \includegraphics[width=\textwidth]{examples/images/ring_with_slit_inhomogeneous.pdf}
    \caption{The output of Code Block~\ref{code:inhomogeneous}: Meissner screening of a uniform applied field of $10\,\mu\mathrm{T}$ by a ring with a slit in a superconducting film with inhomogeneous effective penetration depth $\Lambda(x, y)$. a) The inhomogeneous effective penetration depth $\Lambda(x, y)$, with the ring's outline overlaid in orange. b) The current density $\vec{J}$ in the ring, generated with \inline{Solution.plot_currents()}. c) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated with \inline{Solution.plot_fields()}. d) The $z$-component of the magnetic field evaluated $z=0.5\,\um$ above the ring (generated using \inline{Solution.plot_field_at_positions()}).}
    \label{fig:inhomogeneous}
\end{figure*}

>>>>

\subsection{Pearl vortices in thin films}
\label{section:examples:pearl-vortices}
Vortices trapped in 2D superconductors ($d\ll\lambda$, where $d$ is the film thickness and $\lambda$ is the London penetration depth), i.e. ``Pearl vortices,'' are associated with different current and magnetic field distributions than Abrikosov vortices trapped in bulk type-II superconductors~\cite{Pearl1964-cl}. The 2D Fourier transform $\tilde{H}_z(\vec{k}, z)$ of the out-of-plane component of the magnetic field $H_z(\vec{r}, z)$ from a Pearl vortex located at the origin $x=y=z=0$ is given by
\begin{equation}
    \tilde{H}_z(\vec{k}, z)=\mathcal{F}\{H_z(\vec{r}, z)\}=\frac{1}{\mu_0}\frac{\Phi_0e^{-|\vec{k}|z}}{1+2\Lambda|\vec{k}|},
    \label{eq:pearl}
\end{equation}
where $\mathcal{F}\{\cdot\}$ is the 2D Fourier transform, $\vec{k}=(k_x, k_y)$ are in-plane spatial frequencies, $z$ is the out-of-plane position at which the field is evaluated, and $2\Lambda = 2\lambda^2 / d$ is the Pearl length~\cite{Pearl1964-cl, Tafuri2004-ap}. The real-space magnetic field distribution near a Pearl vortex can be calculated numerically by taking the inverse Fourier transform of Eq.~\ref{eq:pearl}: $H_z(\vec{r}, z)=\mathcal{F}^{-1}\{\tilde{H}_z(\vec{k}, z)\}$.

To include vortices in a \SuperScreen model, one can simply input a \inline{list} of \inline{superscreen.Vortex} objects when calling \inline{superscreen.solve()} (see Code Block~\ref{code:pearl-vortex}). A \inline{Vortex} object specifies the $x,y$ position for the vortex core, the name of the superconducting layer in which the vortex is pinned, and the number of flux quanta $\Phi_0$ contained in the vortex (which is 1 by default). The field distributions generated by \SuperScreen in the presence of vortices as described in Sections~\ref{section:model:vortices} and~\ref{section:implementation} agree to within a few percent with the distributions obtained using this Fourier transform method, as demonstrated in Code Block~\ref{code:pearl-vortex} and Figure~\ref{fig:pearl}(c-e). See Ref.~\cite{Brandt2005-wj} for a method to compute the self-energy and interaction energies of vortices in thin films.

@@

\begin{figure*}[h!]
    \centering
    \includegraphics[width=\textwidth]{examples/images/pearl.png}
    \caption{Vortex field profiles calculated with \SuperScreen agree with the analytical solution (Eq.~\ref{eq:pearl}) to within a few percent. Here, we model a vortex trapped at the center of a square superconducting film lying in the $x-y$ plane with side length $20\,\um$ as a function of the film's effective penetration depth, $\Lambda$. (a) Cross section along the $x$-axis of the out-of-plane magnetic field $\mu_0H_z$ from the vortex, evaluated at a vertical distance $z=1\,\um$ above the film. The inset shows the vortex field profile for $\Lambda=0\,\um$ evaluated at $z=1\,\um$, with a dashed white line indicating the cross-section axis. (b) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $x$-axis cut shown in (a). (c) Cross-section along the $z$-axis of $\mu_0H_z$ directly above the center of the vortex (logarithmic $y$ axis scale). (d) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $z$-axis cut shown in (c). In (a) and (c), the results from \SuperScreen are shown as open circles and the results from the Fourier transform method are shown as solid lines. (e) The fluxoid $\Phi_S^f$ for a circular region in the film with radius $r=1\,\um$ centered on the vortex core. As $\Lambda$ increases, so to does the supercurrent contribution to the fluxoid. (f) Error in the total simulated fluxoid relative to $\Phi_0$: error = $(\Phi_S^f(\Lambda) - \Phi_0) / \Phi_0$.}
    \label{fig:pearl}
\end{figure*}

@@

Figure~\ref{fig:pearl}(e) shows the fluxoid for a circular region $S$ with radius $r=1\,\um$ enclosing a Pearl vortex trapped in a film as a function of the film's effective penetration depth, $\Lambda$. When $\Lambda=0$, the screening currents decay very quickly away from the center of the vortex, so the ``supercurrent part'' of the $\Phi^f_S$ vanishes. With increasing $\Lambda$, the ``supercurrent part'' accounts for an increasing fraction of the total fluxoid.

@@

\subsection{Application: scanning SQUID susceptometry}
\label{section:examples:scanning-squid}

In scanning superconducting quantum interference device (SQUID) susceptometry\cite{Gardner2001-gr, Huber2008-il, Kirtley_Kalisky_2012}, the diamagnetic susceptibility of a superconducting sample is measured by bringing the sample close to a pair of superconducting loops. The first loop, called the ``pickup loop" (PL) is attached to a SQUID circuit that sensitively measures the magnetic flux threading the loop. The second loop, called the ``field coil" (FC), carries a known current and applies a known magnetic field to both the pickup loop and the sample. The superconducting sample screens the magnetic field from the field coil, modifying the amount of flux threading the pickup loop. Thus the change in mutual inductance $M_\mathrm{PL-FC}$ between the field coil and pickup loop in the presence of a sample provides a measure of the sample's magnetic susceptibility. For superconducting samples, this diamagnetic response is a measure of the sample's penetration depth and therefore its superfluid density.

As shown in Ref.~\cite{Brandt2005-wj}, the mutual inductance $M_{ij}$ between holes $i$ and $j$ in a superconducting structure is given by
\begin{equation}
    M_{ij}=\frac{\Phi^f_{S_i}}{I_j},
\end{equation}
where $\Phi^f_{S_i}$ is the fluxoid for a region $S_i$ containing the hole $i$, and $I_j$ is the current circulating around hole $j$. The mutual inductance values for a set of holes form a mutual inductance matrix. The diagonals of the mutual inductance matrix are the hole self-inductances ($M_{ii}=L_i$, the self-inductance of hole $i$), and the matrix is symmetric ($M_{ij}=M_{ji}$) due to the reciprocity theorem. If the penetration depth of the film containing hole $i$ is $\Lambda = 0$, then no field penetrates the film and the fluxoid $\Phi^f_{S_i}$ is equal to $\Phi_i$, the flux through hole $i$. For a device with $N_h$ holes, the $N_h\times N_h$ mutual inductance matrix $\mathbf{M}$ can be computed using the $\inline{Device.mutual_inductance_matrix()}$ method.

Figure~\ref{fig:squid-mutuals}(a) shows \SuperScreen \inline{Device} models of the field coil and pickup loop region of four types of real SQUID susceptometers, with geometry taken from the layout artwork (GDS) files. In addition to the field coil and pickup loop, there are superconducting shields that limit the amount of magnetic flux that can penetrate the leads connecting the loops to the rest of the circuit (the rest of the circuit is not modeled). There are three relevant layers of superconducting films: the base electrode (BE), which is furthest from the sample contains the field coil; the first wiring layer (W1), which contains the pickup loop and a shield covering the field coil leads; and the second wiring layer (W2), which is closest to the sample and contains a shield covering the pickup loop leads. There are two insulating layers: I1, which separates BE and W1, and I2, which separates W1 and W2. Table~\ref{table:squid-layers} shows the thickness $d$ of each layer in the real devices, as well as the vertical position of the 2D films used to model each layer. For the superconducting layers, which are made of Nb, we take the London penetration depth to be $\lambda = 80\,\nm$. It is important to note that because $\lambda < d$ for all three layers, the susceptometers are not in the 2D limit in which the model described in Section~\ref{section:model} is technically valid. Nevertheless, as shown in Figure~\ref{fig:squid-mutuals}, the field coil - pickup loop mutual inductances, $M_\mathrm{sim}$, computed by \SuperScreen lie within the range of mutual inductances measured in real devices, $M_\mathrm{exp}$ (taken from Ref.~\cite{Kirtley2016-zz} Table 1), for all four sizes of susceptometer.\footnote{The mutual inductance values are shown in units of $\Phi_0 / \mathrm{A}$, where $1\,\Phi_0 / \mathrm{A}\approx2.068\times10^{-3}\,\mathrm{pH}$.} This suggests that variation in current density along the thickness of each film (along the $z$-axis) is not critical in determining the mutual inductance. The convergence of $M_\mathrm{PL-FC}$ as a function of solver iteration (see Section~\ref{section:model:multilayer}) is shown in Figure~\ref{fig:squid-mutuals}(c).

\begin{table*}
\centering
\begin{tabular}{|l|l|l|l|l|}
\hline
Layer name & Material & Thickness & Vertical position, $z_0$ & Films located in layer \\ \hline
\hline
W2 & Nb & $d_\mathrm{W2} = 200\,\nm$ & $d_\mathrm{W2} / 2$ & Pickup loop shield, modulation coil \\ \hline
I2 & SiO${}_2$ & $d_\mathrm{I2} = 130\,\nm$ & --- & --- \\ \hline
W1 & Nb & $d_\mathrm{W1} = 100\,\nm$ & $d_\mathrm{W2} + d_\mathrm{I2} + d_\mathrm{W1} / 2$ & Pickup loop, field coil shield \\ \hline
I1 & SiO${}_2$ & $d_\mathrm{I1} = 150\,\nm$ & --- & --- \\ \hline
BE & Nb & $d_\mathrm{BE} = 160\,\nm$ & $d_\mathrm{W2} + d_\mathrm{I2} + d_\mathrm{W1} + d_\mathrm{I1} + d_\mathrm{BE} / 2$ & Field coil, pickup loop shield \\ \hline
\end{tabular}
\caption{Layer stackup for the SQUID susceptometers discussed in Section~\ref{section:examples:scanning-squid}. W2 is located at the surface of the chip (deposited last, closest to the sample) and BE deepest below the chip's surface (deposited first). See Refs.~\cite{Kirtley2016-zz, Kirtley2016-gt} for more details on the designed of the suscpetometers.}
\label{table:squid-layers}
\end{table*}

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{examples/images/squid-mutuals.png}
    \caption{Calculating SQUID susceptometer mutual inductance, defined as the fluxoid induced in the SQUID pickup loop per unit current flowing in the field coil: $M_\mathrm{PL-FC}=\Phi^f_\mathrm{PL} / I_\mathrm{FC}$. Top row (a): Schematics of \SuperScreen models for the field coil and pickup loop region of four sizes of scanning SQUID susceptometer (generated using \inline{Device.draw()}) with pickup loop inner radii ranging from $0.1\,\um$ (``Small'') to $3\,\um$ (``X-Large''). The wiring layers BE, W1, and W2 are shown in blue, orange, and green respectively. Middle row (b): Simulated magnetic field $\mu_0H_z$ evaluated at the plane of layer W1, which contains the pickup loop, normalized by the current $I_\mathrm{FC}$ flowing in the field coil (which is located in layer BE). Bottom row (c): Convergence of the four models, defined as the fractional change in mutual inductance between subsequent iterations $i$. For all four models, the simulated mutual inductance, $M_\mathrm{sim}$, falls within the range of mutual inductance values measured in real devices, $M_\mathrm{exp}$, which were reported in Table 1 of Ref.~\cite{Kirtley2016-zz}. The meshes for the ``Small,'' ``Medium,'' and ``Large'' models consisted of approximately 5,000 vertices and 10,000 triangles, whereas the mesh for the ``X-Large'' model consisted of about 7,700 vertices and 15,000 triangles. The two smaller models converge more quickly than the two larger models for reasons discussed in \ref{appendix:numerics}. Note that for the ``X-Large'' model, we set the thicknesses of layers I1 and I2 both to 300 nm to ensure convergence (see \ref{appendix:numerics} and Figure~\ref{fig:xlarge-dz-dr}).}
    \label{fig:squid-mutuals}
\end{figure*}

Having established the value of the field coil - pickup loop mutual inductance $M_\mathrm{PL-FC}$ in the absence of a sample, we can simulate a scanning SQUID susceptometry measurement by calculating $M_\mathrm{PL-FC}$ in the presence of a superconducting sample as a function of the relative position of the pickup loop and the sample. For example, in Figure XX, we simulate a SQUID susceptometry image of of a ``Large'' susceptometer (the sample) measured with a ``Medium'' suceptometer (the sensor). Given a \inline{Device} representing the sensor and a \inline{Device} representing the sample, this calculation is performed in three steps:
\begin{enumerate}
    \item{Simulate the sensor with some known current $I_\mathrm{FC}$ circulating in the field coil to get \inline{field_coil_solution}.}
    \item{For a given relative position $(x_s, y_s)$ between the sensor and sample, simulate the sample with an applied field given by \inline{field_coil_solution.field_at_position()} to get \inline{sample_solution}.}
    \item{Simulate the sensor again, this time with the applied field given by \inline{sample_solution.field_at_position()}, and evaluate the fluxoid $\Phi^f_\mathrm{PL}$ for the hole representing the sensor's pickup loop, and calculate the mutual inductance: $M_\mathrm{PL-FC}(x_s, y_s)=\Phi^f_\mathrm{PL} / I_\mathrm{FC}$.}
\end{enumerate}
These three steps are repeated for every desired $(x_s, y_s)$ to build up a susceptometry image. Note that in principle it is possible to combine the sensor and sample into a single \inline{Device} with 6 superconducting layers, however this is impractical because it would require generating a new mesh for each $(x_s, y_s)$ and, as discussed in detail in \ref{appendix:numerics}, the problem scales unfavorably with the number of layers in a device and with the total lateral extent of a device.

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{}
    \caption{Caption}
    \label{fig:my_label}
\end{figure}

\subsection{Application: scanning SQUID magnetometry}
\label{section:examples:magnetometry}

@@

Third, \SuperScreen does not support ``terminal currents,'' i.e. currents flowing in one terminal of a device and out another terminal. This means that inductance calculations are limited to structures with holes, in which all applied currents are circulating currents associated with trapped flux (see Sections~\ref{section:model:holes} and~\ref{section:examples:scanning-squid}). Terminal currents can, however, be included in stream function-base models by setting appropriate boundary conditions~\cite{Khapaev1997-kw,Khapaev2001-xq,Khapaev2001-pw,Muller2021-ci}. Finally, care should be taken to ensure that for a given model the mesh is of sufficient density that, to within the desired precision, the results of simulations do not depend on mesh size (see \ref{appendix:numerics}).

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{examples/images/ring_with_slit_inhomogeneous.pdf}
    \caption{The output of Code Block~\ref{code:inhomogeneous}: Meissner screening of a uniform applied field of $10\,\mu\mathrm{T}$ by a ring with a slit in a superconducting film with inhomogeneous effective penetration depth $\Lambda(x, y)$. a) The inhomogeneous effective penetration depth $\Lambda(x, y)$, with the ring's outline overlaid in orange. b) The current density $\vec{J}$ in the ring, generated with \inline{Solution.plot_currents()}. c) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated with \inline{Solution.plot_fields()}. d) The $z$-component of the magnetic field evaluated $z=0.5\,\um$ above the ring (generated using \inline{Solution.plot_field_at_positions()}).}
    \label{fig:inhomogeneous}
\end{figure*}
